A Kochen-Specker system has at least 21 vectors\\ {\small (extended abstract)}

### 2014-09-08 paper/main.tex
Move paper into subdirectory
paper: convert to eptcs

\documentclass[a4paper]{article}

\usepackage{algorithm2e}
\usepackage{hyperref}
\usepackage{paralist}
\usepackage{graphicx}
\usepackage{authblk}
\usepackage{amsmath}
\usepackage{wrapfig}
\usepackage{amsthm}

%\usepackage{draftwatermark}

@@

\title{A Kochen-Specker system has at least 21 vertices\\
        {\small (extended abstract)}}

\author{Sander Uijlen}
\author{Bas Westerbaan}

% TODO will we keep these @cs.ru.nl addresses?
\affil{{\small Institute for Computing and Information Sciences\\
        Radboud Universiteit Nijmegen}\\
   \{\texttt{suijlen},\texttt{bwesterb}\}\texttt{@cs.ru.nl}}

@@

We have verified the main result of \cite{aow11}:
\begin{comp}
There is a unique non-010-colorable squarefree connected graph on~$17$ or less
vertices:
\begin{center}
\includegraphics[width=50mm]{graphs/c17.jpg}
\end{center}
It is not embeddable, as the graph in Figure~\ref{fig:unemb-10-2}
is an unembeddable subgraph.  For our proof,
see Proposition~\ref{prop:unemb-10-2}.
Hence a Kochen-Specker
system has at least 18 points.
\end{comp}

@@

\section{Embeddability}
\label{sec:emb}
\begin{wrapfigure}{r}{0.40\textwidth}
\begin{center}
\includegraphics[width=50mm]{graphs/unemb-10-2.jpg}
\end{center}
\caption{One of the two minimal
        non-embeddable graphs
\label{fig:unemb-10-2}}
\end{wrapfigure}

@@

With this method, we have decided in an hour the embeddability
of every squarefree graph with minimal vertex order three of 13
vertices of less.
In particular:
\begin{comp}\label{comp:unemb20}
    Every squarefree graph of minimal vertex order three
    that is not 010-colorable
    of order less than or equal to 20
    contains, as a subgraph, one of the following three graphs:
    \begin{center}
        \includegraphics[width=120mm]{graphs/unemb-base-20.jpg}
    \end{center}
    These three graphs are unembeddable.  The left and middle graph
    are the only minimal unembeddable squarefree graph.
\end{comp}
For the first graph, we have proven directly that it is unembeddable.
See Proposition~\ref{prop:unemb-10-2}.
For the second graph, we also have a similar direct proof. The third graph is shown to not be embeddable using our algorithm.

@@

% attribute mckay for answering questions?
% TODO attribute geng
\clearpage
\bibliography{main}{}
\bibliographystyle{plain}

>>>>

\documentclass[adraft,copyright,creativecommons]{eptcs}

\usepackage{algorithm2e}
\usepackage{breakurl}
\usepackage{hyperref}
\usepackage{paralist}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{wrapfig}
\usepackage{amsthm}

@@

\title{A Kochen-Specker system has at least 21 vectors\\
        {\small (extended abstract)}}
\def\titlerunning{A Kochen-Specker system has at least 21 vectors
            (extended abstract)}
\def\authorrunning{Uijlen \& Westerbaan}

\author{Sander Uijlen
    \institute{Radboud Universiteit}
    \email{suijlen@cs.ru.nl}
\and
    Bas Westerbaan
    \institute{Radboud Universiteit}
    \email{bwesterb@cs.ru.nl}}

@@

We have verified the main result of \cite{aow11}:
\begin{comp}
There is a unique non-010-colorable squarefree connected graph on~$17$ or less
vertices:
\begin{center}
\includegraphics[width=50mm]{../graphs/c17.jpg}
\end{center}
It is not embeddable, as the graph in Figure~\ref{fig:unemb-10-2}
is an unembeddable subgraph.  For our proof,
see Proposition~\ref{prop:unemb-10-2}.
Hence a Kochen-Specker
system has at least 18 points.
\end{comp}

@@

\section{Embeddability}
\label{sec:emb}
\begin{wrapfigure}{r}{0.40\textwidth}
\begin{center}
\includegraphics[width=50mm]{../graphs/unemb-10-2.jpg}
\end{center}
\caption{One of the two minimal
        non-embeddable graphs
\label{fig:unemb-10-2}}
\end{wrapfigure}

@@

With this method, we have decided in an hour the embeddability
of every squarefree graph with minimal vertex order three of 13
vertices of less.
In particular:
\begin{comp}\label{comp:unemb20}
    Every squarefree graph of minimal vertex order three
    that is not 010-colorable
    of order less than or equal to 20
    contains, as a subgraph, one of the following three graphs:
    \begin{center}
        \includegraphics[width=120mm]{../graphs/unemb-base-20.jpg}
    \end{center}
    These three graphs are unembeddable.  The left and middle graph
    are the only minimal unembeddable squarefree graph.
\end{comp}
For the first graph, we have proven directly that it is unembeddable.
See Proposition~\ref{prop:unemb-10-2}.
For the second graph, we also have a similar direct proof. The third graph is shown to not be embeddable using our algorithm.

@@

% attribute mckay for answering questions?
% TODO attribute geng
\clearpage
\bibliography{main}{}
\bibliographystyle{eptcs}
